The YUIMA Project: a Computational Framework for Simulation and Inference of Stochastic Differential Equations

### 2011-10-15 pkg/yuimadocs/inst/doc/JSS/article.Rnw
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/yuima@192 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
update
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/yuima@193 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Alexandre Brouste, Stefano M. Iacus, Hiroki Masuda, Masayuki Uchida, Nakahiro Yoshida} %% comma-separated
\Plaintitle{A Capitalized Title: Something About a Package foo} %% without formatting
\Shorttitle{A Capitalized Title} %% a short title (if necessary)

@@

\noindent
In this case, the appropriate slot is now filled
@ 
{\scriptsize
<<>>=
str(mod4)
@
}

@@

\section*{Acknowledgements}
The YUIMA Project was initially started by Nakahiro Yoshida as principal 
investigator and then Stefano M. Iacus joined as coordinator of the \proglang{R}
implementation. \textcolor{red}{PLEASE ADD SOME HISTORICAL FACTS AND ACKNOWLEDGMENTS OF DIFFERENT FUNDS}.

>>>>

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Alexandre Brouste, Stefano M. Iacus, Hiroki Masuda, Masayuki Uchida, Nakahiro Yoshida} %% comma-separated
\Plaintitle{YUIMA: Simulation and Inference for SDE} %% without formatting
\Shorttitle{The YUIMA Project} %% a short title (if necessary)

@@

\noindent
In this case, the appropriate slot is now filled
@ 
{\scriptsize
<<>>=
str(mod4)
@
}
The user can choose between the two simulation schemes, namely the Cholesky method and \citet{WoodChan} method.

@@

%\section*{Acknowledgements}
%The YUIMA Project was initially started by Nakahiro Yoshida as principal 
%investigator and then Stefano M. Iacus joined as coordinator of the \proglang{R}
%implementation. \textcolor{red}{PLEASE ADD SOME HISTORICAL FACTS AND ACKNOWLEDGMENTS OF DIFFERENT FUNDS}.
